On the computational complexity of detecting possibilistic locality

### 2017-06-28 paper.tex
More careful explanation of why we consider only clauses of the forms shown- i.e. they are fully general.

\begin{thm}
The \textsc{(2,3)-PossLoc} decision problem is \textbf{NP}-complete.
\end{thm}
\begin{proof}
\begin{defn}
\textsc{0(1)-valid 3-SAT} is the set of \textsc{3-SAT} decision problems that are satisfied by assigning a value of 0 (1) to all variables.
\end{defn}

\begin{lem}\label{rob3sat}
\textsc{2-Robust 0-valid 1-valid 3-SAT} is \textbf{NP}-complete.
\end{lem}
\begin{proof}[Proof of Lemma]
Consider a general \textsc{3-SAT} instance $C=\bigwedge_i c_i$, where $c_i$ are clauses consisting of the disjunction of three literals or negated literals. We will introduce two new variables $x$ and $y$, and apply the mapping $f$ to each clause $c_i$ defined by:
\begin{equation}
f(l_1\cup l_2 \vee  \circ  l_3) = (l_1\vee l_2 \vee \circ l_3 \vee \neg x),
\end{equation}
\begin{equation}
f(\neg l_1\vee\neg l_2 \vee \circ  l_3) = (\neg l_1\cup\neg l_2 \vee \circ  l_3 \vee  y),
\end{equation}
in which the $\circ$ symbol is being used to denote the presence or absence of a $\neg$ symbol. We note that now, every clause of $C'=\bigwedge_i f(c_i)$ contains at least one positive literal and at least one negative literal, and so $C'$ is both 0-valid and 1-valid.

>>>>

\begin{thm}
The \textsc{(2,3)-PossLoc} decision problem is \textbf{NP}-complete.
\end{thm}
\begin{proof}
We will now introduce the notion of 0- and \textsc{1-valid 3-SAT}. This restriction is not strictly necessary for  this proof, but we will see later that it has a bearing on the computational hardness of deciding locality for quantum-mechanically accessible possibilitiy tables.
\begin{defn}
\textsc{0-valid 3-SAT} is the set of \textsc{3-SAT} decision problems that are satisfied by assigning a value of 0 to all variables.
\end{defn}
We will define \textsc{1-valid 3-SAT} analagously.
\begin{lem}\label{rob3sat}
\textsc{2-Robust 0-valid 1-valid 3-SAT} is \textbf{NP}-complete.
\end{lem}
\begin{proof}[Proof of Lemma]
Consider a general \textsc{3-SAT} instance $C=\bigwedge_i c_i$, where $c_i$ are clauses consisting of the disjunction of three literals or negated literals. We will introduce two new variables $x$ and $y$, and apply the mapping $f$ to each clause $c_i$ defined by:
\begin{equation}
f(l_1\cup l_2 \vee  \circ  l_3) = (l_1\vee l_2 \vee \circ l_3 \vee \neg x),
\end{equation}
\begin{equation}
f(\neg l_1\vee\neg l_2 \vee \circ  l_3) = (\neg l_1\cup\neg l_2 \vee \circ  l_3 \vee  y),
\end{equation}
in which the $\circ$ symbol is being used to denote the presence or absence of a $\neg$ symbol. By the pigeonhole principle, each clause must contain either at least two positive literals, or at least two negated literals, and so this mapping is defined uniquely between \textsc{3-SAT} and \textsc{4-SAT} instances. We note that now, every clause of $C'=\bigwedge_i f(c_i)$ contains at least one positive literal and at least one negative literal, and so $C'$ is both 0-valid and 1-valid.
